---
title: "Behavioural_R"
output:
  pdf_document: default
  html_document: default
date: "2025-04-16"
---

# Behavioural Data Analysis - Experiment 1 (Garcia quasi replication)
```{r}
# libraries % file
library(tidyverse)
library(rstatix)
library(ggpubr)
library(lme4)
library(lmerTest)
library(ggplot2)
library(dplyr)
library(effsize)  # for Cohen's d
library(tidyr)
library(dplyr)
library(rstatix) # also for cohen's d
library(effectsize)
library(purrr)
library(dplyr)
install.packages("afex")
library(afex)
library(dplyr)
library(emmeans)
library(dplyr)
library(rstatix)
library(ez)
library(dplyr)
library(gt)



file <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/data/data_sets/GarciaParticipants_Eye_Response_Feed_Allfix_addm_OV_Abs.csv"

data <- read.csv(file)
```
# Filter phases, get mean, remove outliers, check normality
```{r}
# phases
phases<- c("LE", "ES", "EE")
excluded_subs <- c(6,99)   # exclusion of participants from behavioral data: Nr.6 stopped experiment at the start, 99 is me; if we exclude participants due to lack of eye-tracking data, it would be 4,5,6,14     1, 4, 5, 6, 14, 99

data_filt <- data %>%
  filter(phase %in% phases & !sub_id %in% excluded_subs)

# mean accuracy per participant and phase
accuracy_df <- data_filt %>%
  group_by(sub_id, phase) %>%
  summarise(Mean_Accuracy = mean(corr), .groups = "drop")

# removing outliers
outliers <- accuracy_df %>%
  group_by(phase) %>%
  identify_outliers(Mean_Accuracy)
accuracy_df <- accuracy_df %>%
  filter(!(sub_id %in% outliers$sub_id[outliers$is.extreme]))

# normality assumption test
shapiro_results_corr <- accuracy_df %>%
  group_by(phase) %>%
  summarise(Shapiro_p = shapiro.test(Mean_Accuracy)$p.value)
```

# Accuracy per choice problem in the LE phase

```{r}
# get the accuracy for each difficulty level in the LE phase (10/30, 20/60, 40/80, 70/90)

fig_out <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/Figures/Garcia_EXP_Mean_Acc_LE_cond.pdf"    

learning_cond <- c(3, 2, 1, 0)

learning_acc_df <- data %>%
  filter(phase == "LE", cond %in% learning_cond, !sub_id %in% excluded_subs) %>%
  group_by(sub_id, cond) %>%
  summarise(mean_acc_LE = mean(corr), .groups = "drop") %>%
  mutate(cond = factor(cond, 
                       levels = c(3, 2, 1, 0),
                       labels = c("40/60", "30/70", "20/80", "10/90")),
                       cond_num = as.numeric(cond),
                       jittered_x = cond_num + runif(n(), -0.10, 0.10))

mean_points_LE <- learning_acc_df %>%
  group_by(cond) %>%
  summarise(mean_val = mean(mean_acc_LE), .groups = "drop")

cond_colors <- c(
  "40/60" = "rosybrown1",
  "30/70" = "rosybrown2",
  "20/80" = "rosybrown3",
  "10/90" = "rosybrown4"
)

learning_acc_plot <- ggplot() +
  geom_boxplot(data = learning_acc_df, aes(x = cond, y = mean_acc_LE, fill = cond),
               width = 0.55, outlier.shape = NA, alpha = 0.7) +
  geom_line(data = learning_acc_df, aes(x = jittered_x, y = mean_acc_LE, group = sub_id),
            color = "black", alpha = 0.05) +
  geom_point(data = learning_acc_df, aes(x = jittered_x, y = mean_acc_LE),
             color = "black", size = 2, alpha = 0.3) +
  geom_text(data = mean_points_LE, aes(x = cond, y = mean_val, label = "*"),
            color = "red", size = 10, fontface = "bold") +
  scale_fill_manual(values = cond_colors, guide = "none") +
  labs(
    title = "Mean Accuracy Across Blocks in the LE Phase",
    x = "Condition",
    y = "Mean Accuracy (%)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(color = "gray80", size = 0.3),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.ticks.length = unit(4, "pt"),
    axis.line = element_blank(),
    plot.title = element_text(size = 18),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18),
    axis.text.x = element_text(size = 18, color = "black"),
    axis.text.y = element_text(size = 18, color = "black") 
)

ggsave(filename = fig_out, plot = learning_acc_plot, width = 8, height = 6, dpi = 300)
learning_acc_plot

```

# Mean accuracy per learning block stats

```{r}
# maakign cond  factor
learning_acc_df <- learning_acc_df %>%
  mutate(cond = factor(cond, levels = c("40/60", "30/70", "20/80", "10/90")))

ez_out <- ezANOVA(
  data        = learning_acc_df,
  dv          = .(mean_acc_LE),
  wid         = .(sub_id),
  within      = .(cond),
  type        = 3,
  detailed    = TRUE     
)

print(ez_out)

##########################################################################
posthoc <- learning_acc_df %>%
  pairwise_t_test(
    mean_acc_LE ~ cond,
    paired         = TRUE,
    p.adjust.method = "bonferroni",
    conf.level      = 0.95,        
    detailed        = TRUE         
  )

posthoc

learning_acc_df %>%
  group_by(cond) %>%
  summarise(
    n         = n(),
    mean_acc  = mean(mean_acc_LE),
    sd_acc    = sd(mean_acc_LE),
    sem_acc   = sd_acc / sqrt(n),
    .groups   = "drop"
  )

# posthoc table
posthoc_tbl <- posthoc %>%
  mutate(
    contrast  = paste(group1, "–", group2),
    estimate  = round(estimate, 2),
    statistic = round(statistic, 2),
    conf.low  = round(conf.low, 2),
    conf.high = round(conf.high, 2),
    p.adj     = round(p.adj, 2)
  ) %>%
  select(contrast, estimate, conf.low, conf.high, statistic, df, p.adj)

write.csv(
  posthoc_tbl,
  "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/garcia_table_LE.csv",
  row.names = FALSE
)


# Descriptive stats table: mean and SE per condition
desc_tbl <- learning_acc_df %>%
  group_by(cond) %>%
  summarise(
    n        = n(),
    mean_acc = mean(mean_acc_LE),
    sd_acc   = sd(mean_acc_LE),
    sem_acc  = sd_acc / sqrt(n),
    .groups  = "drop"
  ) %>%
  mutate(
    mean_acc = round(mean_acc, 2),
    sd_acc   = round(sd_acc, 2),
    sem_acc  = round(sem_acc, 2)
  )

# Save descriptive table as CSV
write.csv(
  desc_tbl,
  "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/garcia_table_LE_descriptives.csv",
  row.names = FALSE
)
```



# Mean RT per learning block
```{r}

learning_rt_df <- data %>%
  filter(phase == "LE",
         cond %in% learning_cond,
         !sub_id %in% excluded_subs) %>%
  group_by(sub_id, cond) %>%
  summarise(mean_rt_LE = mean(rtime) * 1000,   
            .groups = "drop") %>%
  mutate(cond = factor(cond, levels = c(3, 2, 1, 0),
                       labels = c("40/60", "30/70", "20/80", "10/90")),
         cond_num  = as.numeric(cond),
         jittered_x = cond_num + runif(n(), -0.10, 0.10))
# with the red mean point
mean_points_rt <- learning_rt_df %>%
  group_by(cond) %>%
  summarise(mean_val = mean(mean_rt_LE), .groups = "drop")

learning_rt_plot <- ggplot() +
  geom_boxplot(data = learning_rt_df,aes(x = cond, y = mean_rt_LE, fill = cond), width = 0.55, outlier.shape = NA, alpha = 0.7) +
  geom_line(data = learning_rt_df,aes(x = jittered_x, y = mean_rt_LE, group = sub_id), color = "black", alpha = 0.3) +
  geom_point(data = learning_rt_df,aes(x = jittered_x, y = mean_rt_LE),color = "black", size = 2, alpha = 0.7) +
  geom_text(data = mean_points_rt,aes(x = cond, y = mean_val, label = "*"),color = "red", size = 10, fontface = "bold") +
  scale_fill_manual(values = cond_colors, guide = "none") +
  labs(title = "Mean Reaction Time Across Blocks in the LE Phase",x = "Condition",y = "Mean Reaction Time (ms)") +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(color = "gray80", size = 0.4),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.ticks.length = unit(4, "pt"),
    axis.line = element_blank(),
    plot.title = element_text(size = 18, face = "bold"),
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.x  = element_text(size = 14, color = "black"),
    axis.text.y  = element_text(size = 14, color = "black")
  )
fig_out_rt <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/Figures/Garcia_EXP_Mean_RT_LE_cond.pdf"
ggsave(filename = fig_out_rt, plot = learning_rt_plot,
       width = 8, height = 6, dpi = 300)
learning_rt_plot

```

# Mean RT per learning block 
```{r}
learning_rt_df <- data %>% 
  filter(phase == "LE",cond %in% learning_cond,!sub_id %in% excluded_subs) %>%
  mutate(logRT = log(rtime)) %>% 
  group_by(sub_id, cond) %>% 
  summarise(mean_logRT = mean(logRT),
            .groups = "drop") %>% 
  mutate(cond = factor(cond,
                       levels = c(3, 2, 1, 0),
                       labels = c("40/60", "30/70", "20/80", "10/90")))

ez_rt <- ezANOVA(
  data     = learning_rt_df,
  dv       = .(mean_logRT),
  wid      = .(sub_id),
  within   = .(cond),
  type     = 3,
  detailed = TRUE
)

posthoc_rt <- learning_rt_df %>% 
  pairwise_t_test(
    mean_logRT ~ cond,
    paired          = TRUE,
    p.adjust.method = "bonferroni",
    conf.level      = 0.95,
    detailed        = TRUE
  )

posthoc_rt
exp(posthoc_rt$estimate)

learning_rt_df %>% 
  group_by(cond) %>% 
  summarise(
    n          = n(),
    geo_meanRT = exp(mean(mean_logRT)),     # transform
    sd_logRT   = sd(mean_logRT),
    sem_logRT  = sd_logRT / sqrt(n),
    .groups    = "drop"
  )


```


# Shapiro results
```{r}
# shapiro test results
shapiro_results_corr

```

# Accuracy (LE, ES, EE) + repeated measures ANOVA
```{r}
# repeated measures ANOVA
anova_results <- accuracy_df %>%
  anova_test(dv = Mean_Accuracy, wid = sub_id, within = phase)
anova_table <- get_anova_table(anova_results)

fig_out <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/Figures/Garcia_EXP_Mean_Acc_LE_ES_EE.pdf"       

# summary of rmANOVA
anova_results <- accuracy_df %>%
  anova_test(dv = Mean_Accuracy, wid = sub_id, within = phase)
anova_table <- get_anova_table(anova_results)

#phase + colour
accuracy_df <- accuracy_df %>%
  mutate(phase = factor(phase, levels = c("LE", "ES", "EE")))

phase_colors <- c("EE" = "steelblue1", "ES" = "darkorchid", "LE" = "rosybrown")

plot_df <- accuracy_df %>%
  group_by(sub_id, phase) %>%
  summarise(Mean_Accuracy = mean(Mean_Accuracy), .groups = "drop") %>%
  mutate(
    phase_num = as.numeric(factor(phase, levels = c("LE", "ES", "EE"))),
    jittered_x = phase_num + runif(n(), -0.1, 0.1)
  )

# asterisks
accuracy_summary <- plot_df %>%
  group_by(phase) %>%
  summarise(mean_accuracy = mean(Mean_Accuracy), .groups = "drop")
# plot with horizontal grid
accuracy_plot <- ggplot() +
  geom_boxplot(data = plot_df,aes(x = phase, y = Mean_Accuracy, fill = phase),width = 0.5, alpha = 0.7) +
  geom_line(data = plot_df,aes(x = jittered_x, y = Mean_Accuracy, group = sub_id),color = "black", alpha = 0.05) +
  geom_point(data = plot_df,aes(x = jittered_x, y = Mean_Accuracy),color = "black", size = 2, alpha = 0.3) +
  geom_text(data = accuracy_summary,aes(x = phase, y = mean_accuracy, label = "*"),color = "red", size = 10, fontface = "bold") +
  scale_fill_manual(values = phase_colors) +
  labs(
    title = "Mean Accuracy Across Phases",
    x     = "Phase",
    y     = "Mean Accuracy (%)"
  ) +
  theme_minimal(base_size = 14) +
  scale_y_continuous(
    breaks = seq(0.4, 1, by = 0.2),
    limits = c(0.4, 1),# 0, 0.5, 1.0, 1.5, 2.0
  ) +
  theme(
    panel.grid.major.y = element_line(color = "gray80", size = 0.2),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    axis.ticks.x       = element_line(color = "black"),
    axis.ticks.y       = element_blank(),
    axis.ticks.length  = unit(4, "pt"),
    axis.line          = element_blank(),
    plot.title         = element_text(size = 18),
    axis.title.x       = element_text(size = 18),
    axis.title.y       = element_text(size = 18),
    axis.text.x        = element_text(size = 18,  color = "black"),
    axis.text.y        = element_text(size = 18, color = "black")
  )



accuracy_plot

fig_out <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/Figures/Garcia_EXP_Mean_Acc_LE_ES_EE.pdf"
ggsave(filename = fig_out, plot = accuracy_plot, width = 4, height = 4, dpi = 300)


anova_results %>% get_anova_table()

anova_afex <- aov_ez(id = "sub_id", dv = "Mean_Accuracy", within = "phase", data = accuracy_df)
summary(anova_afex)

# mean and SEM for each phase
accuracy_summary <- accuracy_df %>%
  group_by(phase) %>%
  summarise(mean_accuracy = mean(Mean_Accuracy),sd_accuracy = sd(Mean_Accuracy),n = n(),sem_accuracy = sd_accuracy / sqrt(n))

print(accuracy_summary)
anova_table
```

# Bonferroni Post Hoc Comparisons
```{r}
# Bonferroni post hoc tests
posthoc_results <- accuracy_df %>%
  pairwise_t_test(Mean_Accuracy ~ phase, paired = TRUE, p.adjust.method = "bonferroni", detailed = TRUE)

posthoc_results
names(posthoc_results)

posthoc_results %>% select(group1, group2, p.adj)

wide_df <- accuracy_df %>%
  pivot_wider(id_cols = sub_id,names_from  = phase,values_from = Mean_Accuracy)

cohen.d(wide_df$LE, wide_df$ES, paired = TRUE)  # LE vs ES
cohen.d(wide_df$LE, wide_df$EE, paired = TRUE)  # LE vs EE
cohen.d(wide_df$ES, wide_df$EE, paired = TRUE)  # ES vs EE
```

# Median Accuracy 
```{r}
accuracy_median_summary <- accuracy_df %>%
  dplyr::group_by(phase) %>%
  dplyr::summarise(
    median_accuracy = median(Mean_Accuracy),
    n = dplyr::n()
  )

print(accuracy_median_summary)

```

# Accuracy just between ES & EE

```{r}
es_ee_data <- accuracy_df %>%
  filter(phase %in% c("ES", "EE") & !sub_id %in% excluded_subs)

# Normality check, not sure if I should test these independently, but here we go
shapiro_es <- shapiro.test(es_ee_data %>% filter(phase == "ES") %>% pull(Mean_Accuracy))
shapiro_ee <- shapiro.test(es_ee_data %>% filter(phase == "EE") %>% pull(Mean_Accuracy))
shapiro_es
shapiro_ee

#  if normal ttest, else wilcox. signed rank test
if (shapiro_es$p.value > 0.05 & shapiro_ee$p.value > 0.05) {
  test_res <- es_ee_data %>%
    pairwise_t_test(Mean_Accuracy ~ phase, paired = TRUE, p.adjust.method = "bonferroni")
} else {
  test_res <- es_ee_data %>%
    wilcox_test(Mean_Accuracy ~ phase, paired = TRUE, p.adjust.method = "bonferroni")
}

test_res
```

# Above chance performance ? 

```{r}
phases<- c("LE", "ES", "EE")
excluded_subs <- c(6,99)   # exclusion of participants from behavioral data only (not eye-trcking). Nr.6 stopped experiment at the start, 99 is me; if we exclude participants due to lack of eye-tracking data, it would be 4,5,6,14

data_filt <- data %>%
  filter(phase %in% phases & !sub_id %in% excluded_subs)

# mean accuracy per participant and phase
accuracy_df <- data_filt %>%
  group_by(sub_id, phase) %>%
  summarise(Mean_Accuracy = mean(corr), .groups = "drop")
accuracy_df <- accuracy_df %>%
  mutate(phase = factor(phase, levels = c("LE", "ES", "EE")))

# One-sample t-tests for each phase against chance level
t_test_results <- accuracy_df %>%
  group_by(phase) %>%
  summarise(
    mean_accuracy = mean(Mean_Accuracy),
    se = sd(Mean_Accuracy) / sqrt(n()),
    t_statistic = t.test(Mean_Accuracy, mu = 0.5)$statistic,
    df = t.test(Mean_Accuracy, mu = 0.5)$parameter,
    p_value = t.test(Mean_Accuracy, mu = 0.5)$p.value
  ) %>%
  mutate(
    significance = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01 ~ "**",
      p_value < 0.05 ~ "*",
      TRUE ~ "n.s."
    )
  )
print(t_test_results)

```

# Reaction Time (LE, ES, EE)

```{r}
# get mean rt per participant and phase
rt_df <- data_filt %>%
  group_by(sub_id, phase) %>%
  summarise(Mean_RT = mean(rtime), .groups = "drop")

# outliers chekc
outliers <- rt_df %>%
  group_by(phase) %>%
  identify_outliers(Mean_RT)
rt_df <- rt_df %>%
  filter(!(sub_id %in% outliers$sub_id[outliers$is.extreme]))

# normality assumption? - unnecessary we log trans anyways
shapiro_results_rt <- rt_df %>%
  group_by(phase) %>%
  summarise(Shapiro_p = shapiro.test(Mean_RT)$p.value)
shapiro_results_rt

# mean, sd, sem
rt_summary <- rt_df %>%
  group_by(phase) %>%
  summarise(
    mean_rt = round(mean(Mean_RT), 3),
    sd_rt = round(sd(Mean_RT), 3),
    n = n(),
    sem_rt = round(sd_rt / sqrt(n), 3),
    .groups = "drop"
  )

print(rt_summary)

```

```{r}
aov_rt <- aov_ez(id = "sub_id", dv = "Mean_RT", within = "phase", data = rt_df)

summary(aov_rt) 

```

```{r}
rt_df$log_rt <- log(rt_df$Mean_RT)
aov_log_rt <- aov_ez(id = "sub_id", dv = "log_rt", within = "phase", data = rt_df)
summary(aov_log_rt)

emm <- emmeans(aov_log_rt, ~ phase)
pairs(emm, adjust = "bonferroni")
eta_squared(aov_log_rt, partial = TRUE) 


safe_t_to_d <- possibly(
  function(t, df) {
    d_obj <- t_to_d(t = t, df = df, paired = TRUE)
    as.numeric(d_obj[[1]])  # numeric estimate
  }
)

```

# Additional lmer with log transformed RT
# with lmer we get trial-wise significance 
# using onyly t-test, these RT differences were shadowed with lmer you can account for individual slopes and other individual effects

```{r}
# Wilcoxon signed-rank test with Bonferroni correction
wilcoxon_results <- rt_df %>%
  pairwise_wilcox_test(Mean_RT ~ phase, paired = TRUE, p.adjust.method = "bonferroni")
wilcoxon_results

rt_df$log_rt <- log(rt_df$Mean_RT)
lme_model <- lmer(log_rt ~ phase + (1 | sub_id), data = rt_df)
summary(lme_model)
# post hoc compa
emmeans(lme_model, pairwise ~ phase, adjust = "bonferroni")

```

# RT plot between phases

```{r}
# order
rt_df <- rt_df %>%
  mutate(phase = factor(phase, levels = c("LE", "ES", "EE")))

phase_colors <- c("EE" = "steelblue1", "ES" = "darkorchid", "LE" = "rosybrown")

# summary means for asterisks
rt_summary <- rt_df %>%
  group_by(phase) %>%
  summarise(
    mean_rt = mean(Mean_RT),
    .groups = "drop"
  )

set.seed(123)  
rt_df <- rt_df %>%
  mutate(
    phase_num  = as.numeric(phase),
    jittered_x = phase_num + runif(n(), -0.1, 0.1)
  )

# plot
rt_plot <- ggplot() +
  geom_boxplot(data = rt_df,aes(x = phase, y = Mean_RT, fill = phase),width = 0.5, alpha = 0.7) +
  geom_line(data = rt_df,aes(x = jittered_x, y = Mean_RT, group = sub_id),color = "black", alpha = 0.05) +
  geom_point(data = rt_df,aes(x = jittered_x, y = Mean_RT),color = "black", size = 2, alpha = 0.3) +
  geom_text(data = rt_summary,aes(x = phase, y = mean_rt, label = "*"),color = "red", size = 13, fontface = "bold") +
  scale_fill_manual(values = phase_colors) +
  scale_y_continuous(breaks = seq(0, ceiling(max(rt_df$Mean_RT)*2)/2, by = 0.5)) +
  labs(
    title = "Mean Reaction Time Across Phases",
    x     = "Phase",
    y     = "Mean RT (seconds)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.major.y  = element_line(color = "gray80", size = 0.2),
    panel.grid.major.x  = element_blank(),
    panel.grid.minor    = element_blank(),
    axis.ticks.x        = element_line(color = "black"),
    axis.ticks.y        = element_blank(),
    axis.ticks.length   = unit(4, "pt"),
    axis.line           = element_blank(),
    plot.title          = element_text(size = 18, face = "bold"),
    axis.title.x        = element_text(size = 18, face = "bold"),
    axis.title.y        = element_text(size = 18, ),
    axis.text.x         = element_text(size = 18, color = "black"),
    axis.text.y         = element_text(size = 18, color = "black")
  )

fig_out <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/Figures/Garcia_EXP_Mean_rt_LE_ES_EE.pdf"
ggsave(filename = fig_out, plot = rt_plot, width = 4, height = 4, dpi = 300)
rt_plot

```

```{r}
outliers %>% filter(is.extreme) %>% distinct(sub_id)
# Summary statistics for mean RT per choice type
rtime_summary <- rtime_es %>%
  group_by(choice_type) %>%
  summarise(
    Mean = round(mean(Mean_rtime), 3),
    SD = round(sd(Mean_rtime), 3),
    .groups = "drop"
  )

rtime_summary

```

# Accuracy E vs S choices (ES phase) + Boxplot

```{r}
# Filter ES phase
phases<- c("LE", "ES", "EE")
excluded_subs <- c(6, 99)   # exclusion of participants from behavioral data: Nr.6 stopped experiment at the start, 99 is me; if we exclude participants due to lack of eye-tracking data, it would be 4,5,6,14     1, 4, 5, 6, 14, 99

data_filt <- data %>%
  filter(phase %in% phases & !sub_id %in% excluded_subs)
es_data <- data_filt %>%
  filter(phase == "ES") %>%
  mutate(choice_type = ifelse(stim_chosen == "E", "E", "S"))  

#mean accuracy
accuracy_es <- es_data %>%
  group_by(sub_id, choice_type) %>%
  summarise(Mean_Accuracy = mean(corr), .groups = "drop")

# group
mean_points <- accuracy_es %>%
  group_by(choice_type) %>%
  summarise(
    mean_val = mean(Mean_Accuracy),
    .groups = "drop"
  )

# Normality check
shapiro_e <- shapiro.test(accuracy_es %>% filter(choice_type == "E") %>% pull(Mean_Accuracy))
shapiro_s <- shapiro.test(accuracy_es %>% filter(choice_type == "S") %>% pull(Mean_Accuracy))

shapiro_e
shapiro_s

# normality assumption hold
if (shapiro_e$p.value > 0.05 & shapiro_s$p.value > 0.05) {
  test_accuracy <- accuracy_es %>%
    pairwise_t_test(Mean_Accuracy ~ choice_type, paired = TRUE, p.adjust.method = "bonferroni")
} else {
  test_accuracy <- accuracy_es %>%
    wilcox_test(Mean_Accuracy ~ choice_type, paired = TRUE, p.adjust.method = "bonferroni")
}

test_accuracy

#plot
custom_colors <- c("S" = "#C2185B", "E" = "#0077B6")

set.seed(123)  # for reproducible jitter
accuracy_es <- accuracy_es %>%
  mutate(jittered_x = as.numeric(factor(choice_type)) + runif(n(), min = -0.1, max = 0.1))

acc_es_plot <- ggplot() +
  geom_boxplot(data = accuracy_es,aes(x = choice_type, y = Mean_Accuracy, fill = choice_type),width = 0.5, alpha = 0.7) +
  geom_line(data = accuracy_es,aes(x = jittered_x, y = Mean_Accuracy, group = sub_id),color = "black", alpha = 0.05) +
  geom_point(data = accuracy_es,aes(x = jittered_x, y = Mean_Accuracy),color = "black", size = 2, alpha = 0.3) +
  geom_text(data = mean_points,aes(x = choice_type, y = mean_val, label = "*"),color = "red", size = 10, fontface = "bold") +
  scale_fill_manual(values = custom_colors) +
  labs(
    title = "Accuracy for E and S Choices",
    x     = "Choice Type",
    y     = "Mean Accuracy (%)",
    fill  = "Choice Type"
  ) +
 scale_y_continuous(breaks = seq(0.7, 1, by = 0.1),limits = c(0.7, 1),) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(color = "gray80", size = 0.2),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    axis.ticks = element_line(color = "black"),
    axis.line  = element_blank(),
    plot.title = element_text(size = 18),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18, color = "black"),
    axis.text.x  = element_text(size = 18, color = "black"),
    axis.text.y  = element_text(size = 18, color = "black"),
    legend.text  = element_text(size = 18),
    legend.title = element_text(size = 18)
  )

fig_out <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/Figures/Garcia_EXP_Mean_Acc_E_S_options.pdf"
ggsave(filename = fig_out, plot = acc_es_plot, width = 4, height = 4, dpi = 300)

acc_es_plot

accuracy_es %>%
  group_by(choice_type) %>%
  summarise(mean_acc = mean(Mean_Accuracy),sem_acc = sd(Mean_Accuracy) / sqrt(n()))

t.test(
  x = accuracy_es %>% filter(choice_type == "E") %>% pull(Mean_Accuracy),
  y = accuracy_es %>% filter(choice_type == "S") %>% pull(Mean_Accuracy),
  paired = TRUE)

e_values <- accuracy_es %>% filter(choice_type == "E") %>% pull(Mean_Accuracy)
s_values <- accuracy_es %>% filter(choice_type == "S") %>% pull(Mean_Accuracy)

effect_size <- cohen.d(e_values, s_values, paired = TRUE)
print(effect_size)
```

# Glmer Accuracy E vs S choices (ES phase)
```{r}

# trial-level data for ES phase
es_data_glm <- es_data %>%
  filter(!is.na(corr)) %>%
  mutate(choice_type = factor(choice_type, levels = c("S", "E")))

# logistic mixed model
m1 <- glmer(corr ~ choice_type + (1 | sub_id),data = es_data_glm,family = binomial(link = "logit"),control = glmerControl(optimizer = "bobyqa"))

summary(m1)

# pairwise comparison
emmeans(m1, pairwise ~ choice_type, type = "response")

```


# Median accuracy per choice
```{r}
accuracy_es %>%
  group_by(choice_type) %>%
  summarise(
    median_acc = median(Mean_Accuracy),
    .groups = "drop"
  )

```

# Mean accuracy per choice 
```{r}
accuracy_summary <- accuracy_es %>%
  group_by(choice_type) %>%
  summarise(
    Mean = round(mean(Mean_Accuracy), 3),
    SD = round(sd(Mean_Accuracy), 3),
    .groups = "drop"
  )
accuracy_summary

```

# Mean RT per choice + (ES phase) + Boxplot

```{r}
# Same filter for ES
es_data <- data_filt %>%
  filter(phase == "ES") %>%
  mutate(choice_type = ifelse(stim_chosen == "E", "E", "S"))

rtime_es <- es_data %>%
  group_by(sub_id, choice_type) %>%
  summarise(Mean_rtime = mean(rtime), .groups = "drop")

#log rt
rtime_log <- es_data %>%
  group_by(sub_id, choice_type) %>%
  summarise(logRT = mean(log(rtime)), .groups = "drop")

# Paired t-test
test_rtime <- t.test(
  x = rtime_log %>% filter(choice_type == "E") %>% pull(logRT),
  y = rtime_log %>% filter(choice_type == "S") %>% pull(logRT),
  paired = TRUE
)
test_rtime

# additional lmer
es_data_log <- es_data %>%
  mutate(logRT = log(rtime))

lmer_model <- lmer(logRT ~ choice_type + (1 | sub_id), data = es_data_log)
summary(lmer_model)

colours <- c("S" = "#C2185B", 
             "E" = "#0077B6")

mean_points <- rtime_es %>%
  group_by(choice_type) %>%
  summarise(mean_val = mean(Mean_rtime), .groups = "drop")



set.seed(123)  # for reproducibility
# Jitter by numerical x-position
rtime_es <- rtime_es %>%
  mutate(jittered_x = as.numeric(factor(choice_type)) + runif(n(), -0.1, 0.1))

rt_es_plot <- ggplot() +
  geom_boxplot(data = rtime_es, aes(x = choice_type, y = Mean_rtime, fill = choice_type),width = 0.5, alpha = 0.7) +
  geom_line(data = rtime_es, aes(x = jittered_x, y = Mean_rtime, group = sub_id),color = "black", alpha = 0.05) +
  geom_point(data = rtime_es, aes(x = jittered_x, y = Mean_rtime),color = "black", size = 2, alpha = 0.3) +
  geom_text(data = mean_points,aes(x = choice_type, y = mean_val, label = "*"),size = 13, color = "red", inherit.aes = FALSE) +
  scale_fill_manual(values = colours) +
  labs(title = "Reaction Time for E and S Choices",
       x = "Choice Type", y = "Mean RT (seconds)", fill = "Choice Type") +
  scale_y_continuous(breaks = c(1, 2)) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(color = "gray80", size = 0.2),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    axis.ticks.x      = element_line(color = "black"),
    axis.ticks.y      = element_blank(),
    axis.ticks.length = unit(4, "pt"),
    axis.line         = element_blank(),
    plot.title        = element_text(size = 18),
    axis.title.x      = element_text(size = 18),
    axis.title.y      = element_text(size = 18, color = "black"),
    axis.text.x       = element_text(size = 18, color = "black"),
    axis.text.y       = element_text(size = 18, color = "black"),
    legend.text       = element_text(size = 18),
    legend.title      = element_text(size = 18)
  )

fig_out <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/Figures/Garcia_EXP_Mean_rt_E_S_options.pdf"
ggsave(filename = fig_out, plot = rt_es_plot, width = 4, height = 4, dpi = 300)

rt_es_plot
```

# Median and Men RT per choice

```{r}
median_rt_by_choice <- es_data %>%
  group_by(stim_chosen) %>%
  summarise(Median_RT = median(rtime, na.rm = TRUE), .groups = "drop")

median_rt_by_choice

mean_rt_by_choice <- es_data %>%
  group_by(stim_chosen) %>%
  summarise(Mean_RT = mean(rtime, na.rm = TRUE),
            sd_rt = sd(rtime),
            sem_rt = sd(rtime) / sqrt(n()),
            .groups = "drop")

mean_rt_by_choice
```

# Mean RT cohen's d
```{r}
e_vals <- rtime_es %>% filter(choice_type == "E") %>% arrange(sub_id) %>% pull(Mean_rtime)
s_vals <- rtime_es %>% filter(choice_type == "S") %>% arrange(sub_id) %>% pull(Mean_rtime)

# paired cohens d
cohens_d_result <- cohens_d(x = e_vals, y = s_vals, paired = TRUE)
print(cohens_d_result)
```

# Slope Comparisons from Behavioural MATLAB data
```{r}
#slope data from B. Garcia's code
slope_data <- read.csv("D:/Aberdeen_Uni_June24/cap/THESIS/Basile_Garcia/RetrieveAndCompareAnalysis-cleaning_VW/RetrieveAndCompareAnalysis-cleaning/data/stats/Fig2D_SP_Garcia.csv")

# phases
slope_data <- slope_data %>%
  mutate(
    subject = as.factor(subject),
    modality = factor(modality, levels = c("ES", "EE", "SP"))  
  )

# outliers ? 
slope_data %>%
  group_by(modality) %>%
  identify_outliers(slope)

# normality assumption?
slope_data %>%
  group_by(modality) %>%
  summarise(p_value = shapiro.test(slope)$p.value)

# anova
anova_result <- slope_data %>%
  anova_test(dv = slope, wid = subject, within = modality)
anova_table <- get_anova_table(anova_result)
print(anova_table)

# check sphericity
anova_result$`Sphericity Corrections`

posthoc <- slope_data %>%
  pairwise_t_test(
    slope ~ modality,
    paired = TRUE,
    p.adjust.method = "bonferroni"
  )

print(posthoc)

slope_data %>%
  group_by(modality) %>%
  summarise(
    M = round(mean(slope), 2),
    SD = round(sd(slope), 2)
  )

```

# Slope Comparisons (WITH PIE) from Behavioural MATLAB data
```{r}
#slope data from B. Garcia's code
slope_data <- read.csv("D:/Aberdeen_Uni_June24/cap/THESIS/Basile_Garcia/RetrieveAndCompareAnalysis-cleaning_VW/RetrieveAndCompareAnalysis-cleaning/data/stats/Fig2D_Garcia_with_SP_with_Pie.csv")

# phases
slope_data <- slope_data %>%
  mutate(
    subject = as.factor(subject),
    modality = factor(modality, levels = c("ES", "EE", "SP"))  
  )

# outliers ? 
slope_data %>%
  group_by(modality) %>%
  identify_outliers(slope)

# normality assumption?
slope_data %>%
  group_by(modality) %>%
  summarise(p_value = shapiro.test(slope)$p.value)

# anova
anova_result <- slope_data %>%
  anova_test(dv = slope, wid = subject, within = modality)
anova_table <- get_anova_table(anova_result)
print(anova_table)

# check sphericity
anova_result$`Sphericity Corrections`

posthoc <- slope_data %>%
  pairwise_t_test(
    slope ~ modality,
    paired = TRUE,
    p.adjust.method = "bonferroni"
  )

print(posthoc)

slope_data %>%
  group_by(modality) %>%
  summarise(
    M = round(mean(slope), 2),
    SD = round(sd(slope), 2)
  )

```

# Slope comparisons per objective prob per phase

```{r}
#slope data from B. Garcia's code
data <- read.csv("D:/Aberdeen_Uni_June24/cap/THESIS/Basile_Garcia/RetrieveAndCompareAnalysis-cleaning_VW/RetrieveAndCompareAnalysis-cleaning/data/stats/Fig2C_SP_Garcia.csv") %>%
  mutate(
    subject = as.factor(subject),
    modality = as.factor(modality)
  )

one_sample_tests <- data %>%
  group_by(modality, p_obj) %>%
  summarise(
    t_test = list(t.test(p_est, mu = as.numeric(as.character(unique(p_obj))))),
    d = list(effectsize::cohens_d(p_est, mu = unique(p_obj))),
    sem = sd(p_est) / sqrt(n()),
    .groups = 'drop'
  ) %>%
  mutate(
    t_statistic = map_dbl(t_test, ~ .x$statistic),
    df = map_dbl(t_test, ~ .x$parameter),  
    p_value = map_dbl(t_test, ~ .x$p.value),
    mean_estimate = map_dbl(t_test, ~ mean(.x$data)),
    ci_low = map_dbl(t_test, ~ .x$conf.int[1]),
    ci_high = map_dbl(t_test, ~ .x$conf.int[2]),
    cohen_d = map_dbl(d, ~ if ("Cohens_d" %in% names(.x)) .x$Cohens_d else NA_real_),
    magnitude = map_chr(d, ~ if ("magnitude" %in% names(.x)) .x$magnitude else NA_character_)
    ) %>%
  select(
    modality, p_obj, mean_estimate, sem, ci_low, ci_high,
    t_statistic, df, p_value, cohen_d, magnitude
  )


print(one_sample_tests)

one_sample_tests
```
```{r}

```

