---
title: "Eye_tracking_R"
output:
  pdf_document: default
  html_document: default
date: "2025-04-14"
---

# Eye-tracking Analysis for Study 1 (Garcia quasi replication)

#libraries

```{r}
# Load libraries
library(lme4)
library(lmerTest)
library(tidyverse)
library(ggplot2)
library(svglite)
library(sjPlot)
#install.packages("performance")
library(performance)
library(emmeans)
library(ez)
library(dplyr)
library(Matrix)
library(carData)                  # For plotting mixed model
library(effects)                  # For visualizing model effects
library("Hmisc")
library(rstatix)
library(ggpubr)
library(broom)
library(broom.mixed)
library(jsonlite)


# general rules:
# everything from the ES phase -> darkorchid
# everything from the EE phaes -> deepskyblue
```

# reading in the file

```{r}
file <- "C:/Cluster_Github/HDDM_Vero/data_sets/data_sets_Garcia/GarciaParticipants_Eye_Response_Feed_Allfix_addm_OV_Abs_CCT.csv"
data <- read.csv(file)
```

# Accuracy \~ overall value + absolute value


```{r}
es_data
```

# ES - number of fixations first, middle last fix

```{r}
data
```

# ES - Eye-tracking (choose right, corr, rtime) (similar to CCTs paper)

```{r}
data <- read.csv(file)

# phase ES
phase_filter <- "ES"
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(FixationAdvantage, OVcate_2, chose_right)


output_dir <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/ES_eye_predict/"
dir.create(output_dir)

# dependent variable
dep_var <- "chose_right"  # others: 'corr', 'rtime', 'chose_right'
eye_metrics <- c("DwellTimeAdvantage")  #DwellTimeAdvantage, or FinalFix

data <- data %>%
  filter(phase == "ES" & !sub_id %in% excluded_subs)

data <- data %>%
  mutate(
    OV = OV_2,
    VD = AbsValueDiff_2
  ) %>%
  dplyr::select(-OV_2, -AbsValueDiff_2)



# z-score VD & OV & gaze metrics at  OV Level
data <- data %>%
  group_by(OV) %>%
  mutate(
    VD = scale(VD, center = TRUE, scale = TRUE)[,1],  
    across(all_of(eye_metrics), ~ scale(.x, center = TRUE, scale = TRUE)[,1]) 
  ) %>%
  ungroup()

# z-score VD & eye metrics within individual sub_id
data <- data %>%
  group_by(sub_id) %>%
  mutate(
    VD = scale(VD, center = TRUE, scale = TRUE)[,1], 
    across(all_of(eye_metrics), ~ scale(.x, center = TRUE, scale = TRUE)[,1]) 
  ) %>%
  ungroup()


# loop through eye-tracking metrics
for (eye_metric in eye_metrics) {
  # interaction 
  interaction_term <- paste0("OV:", eye_metric)
  #logistic regression
  #glmer
  model <- glmer(as.formula(paste(dep_var, "~ OV *", eye_metric, "+ (1 | sub_id)")),data = data,family = binomial(link = "logit"))


  stats_file <- paste0(output_dir, "ES_Logistic_Model_", dep_var, "_", eye_metric, ".txt")

  # summary and tab_model
  sink(stats_file)
  cat("### Logistic Mixed Model - ES Phase ###\n\n")
  cat("#### Model Summary ####\n")
  print(summary(model)) 
  cat("\n#### Tab Model Output ####\n")
  print(tab_model(model, transform = NULL))  
  sink()

  #fixed effects + predictor names
  beta_df <- as.data.frame(coef(summary(model)))
  beta_df$Predictor <- rownames(beta_df)
  rownames(beta_df) <- NULL
  colnames(beta_df) <- c("Estimate", "SE", "z", "p", "Predictor")

  # get 95% CI
  beta_df <- beta_df %>%
    mutate(
      CI_Lower = Estimate - 1.96 * SE,  # CI Lower
      CI_Upper = Estimate + 1.96 * SE   # CI Upper
    ) %>%
    filter(Predictor != "(Intercept)") 
  # sig. display can be modified to include numbers
  beta_df <- beta_df %>%
    mutate(
      Significance = case_when(
        p < 0.001 ~ "***",
        p < 0.01 ~ "**",
        p < 0.05 ~ "*",
        TRUE ~ "" 
      )
    )

  # order
  beta_df <- beta_df %>%
  filter(Predictor %in% c(eye_metric, interaction_term))
  beta_df$Predictor <- factor(beta_df$Predictor, levels = c(eye_metric, interaction_term))
  output_path <- paste0(output_dir, "ES_", eye_metric, ".pdf")

  plot_figure <- ggplot(beta_df, aes(x = Predictor, y = Estimate, fill = Predictor)) +
    geom_bar(stat = "identity", alpha = 0.7, color = "black", width = 0.5, linewidth = 1) +
    geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), width = 0.05, color = "black", linewidth = 1) +

    geom_text(aes(y = ifelse(Estimate < 0, CI_Lower - 0.09, CI_Upper + 0.09), 
                  label = Significance),
              color = "black", size = 10, fontface = "bold") +  

    geom_hline(yintercept = 0, color = "black", linewidth = 1) +

    labs(title = paste("OV &", eye_metric, "on Symbolic Choice"),
         x = "", y = "Beta Coefficients") +
    
    scale_fill_manual(values = setNames(rep("darkorchid", 4), c("VD", "OV", eye_metric, interaction_term))) +    
    scale_x_discrete(labels = c("FinalFixLoc" = "FF",
                              "OV:FinalFixLoc" = "OV:FF")) +
    theme_minimal() +
    theme(
      legend.position = "none", 
      panel.grid = element_blank(), 
      axis.line.y = element_line(color = "black", linewidth = 1),  
      axis.line.x = element_blank(),  
      axis.text = element_text(size = 18, color = "black"), 
      axis.title = element_text(size = 18, color = "black"),  
      plot.title = element_text(size = 18, hjust = 0.5, color = "black"), 
      panel.background = element_rect(fill = "white", color = "white"),  
      plot.background = element_rect(fill = "white", color = "white") 
    )

  ggsave(output_path, plot = plot_figure, device = "pdf", width = 3, height = 5, dpi = 300)
  cat("saved log regression plot for", eye_metric, "as PDF at:", output_path, "\n")

}
plot_figure
summary(model)
tab_model(model, transform = NULL)  

```

# EE - Eye-tracking (choose right, corr, rtime)

```{r}
data <- read.csv(file)

# phase ES
phase_filter <- "EE"
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(FixationAdvantage, OVcate_2, chose_right)


output_dir <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/EE_eye_predict/"
dir.create(output_dir, showWarnings = FALSE, recursive = TRUE)

# dependent variable


dep_var <- "chose_right"  # others: 'corr', 'rtime', 'chose_right'

eye_metrics <- c("DwellTimeAdvantage")

data <- data %>%
  filter(phase == "EE" & !sub_id %in% excluded_subs)

data <- data %>%
  mutate(
    OV = OV_2,
    VD = AbsValueDiff_2
  ) %>%
  select(-OV_2, -AbsValueDiff_2)


# z-score VD & OV & gaze metrics at  OV Level
data <- data %>%
  group_by(OV) %>%
  mutate(
    VD = scale(VD, center = TRUE, scale = TRUE)[,1],  
    across(all_of(eye_metrics), ~ scale(.x, center = TRUE, scale = TRUE)[,1]) 
  ) %>%
  ungroup()

# z-score VD & eye metrics within individual sub_id
data <- data %>%
  group_by(sub_id) %>%
  mutate(
    VD = scale(VD, center = TRUE, scale = TRUE)[,1], 
    across(all_of(eye_metrics), ~ scale(.x, center = TRUE, scale = TRUE)[,1]) 
  ) %>%
  ungroup()

# loop through eye-tracking metrics
for (eye_metric in eye_metrics) {
  # interaction 
  interaction_term <- paste0("OV:", eye_metric)
  #logistic regression
  #glmer
  model <- glmer(as.formula(paste(dep_var, "~ OV *", eye_metric, "+ (1 | sub_id)")),data = data,family = binomial(link = "logit"))


  stats_file <- paste0(output_dir, "EE_Logistic_Model_", dep_var, "_", eye_metric, ".txt")

  # summary and tab_model
  sink(stats_file)
  cat("### Logistic Mixed Model - EE Phase ###\n\n")
  cat("#### Model Summary ####\n")
  print(summary(model)) 
  cat("\n#### Tab Model Output ####\n")
  print(tab_model(model, transform = NULL))  
  sink()

  #fixed effects + predictor names
  beta_df <- as.data.frame(coef(summary(model)))
  beta_df$Predictor <- rownames(beta_df)
  rownames(beta_df) <- NULL
  colnames(beta_df) <- c("Estimate", "SE", "z", "p", "Predictor")

  # get 95% CI
  beta_df <- beta_df %>%
    mutate(
      CI_Lower = Estimate - 1.96 * SE,  # CI Lower
      CI_Upper = Estimate + 1.96 * SE   # CI Upper
    ) %>%
    filter(Predictor != "(Intercept)") 
  # sig. display can be modified to include numbers
  beta_df <- beta_df %>%
    mutate(
      Significance = case_when(
        p < 0.001 ~ "***",
        p < 0.01 ~ "**",
        p < 0.05 ~ "*",
        TRUE ~ "" 
      )
    )

  # order
  beta_df <- beta_df %>%
  filter(Predictor %in% c(eye_metric, interaction_term))
  beta_df$Predictor <- factor(beta_df$Predictor, levels = c(eye_metric, interaction_term))
  output_path <- paste0(output_dir, "EE_", eye_metric, ".pdf")

  plot_figure <- ggplot(beta_df, aes(x = Predictor, y = Estimate, fill = Predictor)) +
    geom_bar(stat = "identity", alpha = 0.7, color = "black", width = 0.5, linewidth = 1) +
    geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), width = 0.05, color = "black", linewidth = 1) +

    geom_text(aes(y = ifelse(Estimate < 0, CI_Lower - 0.09, CI_Upper + 0.09), 
                  label = Significance),
              color = "black", size = 10, fontface = "bold") +  

    geom_hline(yintercept = 0, color = "black", linewidth = 1) +

    labs(title = paste("OV &", eye_metric, "on Choosing Right"),
         x = "", y = "Beta Coefficients") +
    
    scale_fill_manual(values = setNames(rep("deepskyblue", 4), c("VD", "OV", eye_metric, interaction_term))) +    
    scale_x_discrete(labels = c("DwellTimeAdvantage" = "DTA",
                              "OV:DwellTimeAdvantage" = "OV:DTA")) +
    theme_minimal() +
    theme(
      legend.position = "none", 
      panel.grid = element_blank(), 
      axis.line.y = element_line(color = "black", linewidth = 1),  
      axis.line.x = element_blank(),  
      axis.text = element_text(size = 18, color = "black"), 
      axis.title = element_text(size = 18, color = "black"),  
      plot.title = element_text(size = 18, hjust = 0.5, color = "black"), 
      panel.background = element_rect(fill = "white", color = "white"),  
      plot.background = element_rect(fill = "white", color = "white") 
    )

  ggsave(output_path, plot = plot_figure, device = "pdf", width = 3, height = 5, dpi = 300)
  cat("saved log regression plot for", eye_metric, "as PDF at:", output_path, "\n")

}
plot_figure
summary(model)
tab_model(model, transform = NULL)  
```


# ES - Dwell-Time Advantage

```{r}

data <- read.csv(file)

# phase ES
phase_filter <- "ES"
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(DwellTimeAdvantage, OVcate_2, chose_right )

data <- data %>% 
  filter(
    phase == phase_filter,
    !sub_id %in% excluded_subjects,
    DwellRight > -1,          # here, we can check if we keep only trials where both sides > 0 ms for gaze
    DwellLeft  > -1
  ) %>% 
  drop_na(DwellTimeAdvantage, OVcate_2, chose_right)


data$OVcate_2 <- factor(data$OVcate_2, levels = c("low", "medium", "high"))

# Quantile Binning of DwellTimeAdvantage
data <- data %>%
  group_by(sub_id, OVcate_2) %>%
  mutate(DwellTimeAdvantage_bin = cut(DwellTimeAdvantage, 
                                      breaks = unique(quantile(DwellTimeAdvantage, probs = seq(0, 1, length.out = 6), na.rm = TRUE)), 
                                      labels = 1:(length(unique(quantile(DwellTimeAdvantage, probs = seq(0, 1, length.out = 6), na.rm = TRUE))) - 1),
                                      include.lowest = TRUE)) %>%
  ungroup()



summary_df <- data %>%
  group_by(DwellTimeAdvantage_bin, OVcate_2) %>%
  summarise(
    p_choose_right = mean(chose_right, na.rm = TRUE),       # mean 
    ci = 1.96 * sd(chose_right, na.rm = TRUE) / sqrt(n()),  # 95% CI
    .groups = 'drop'
  )

# bin order 
summary_df$DwellTimeAdvantage_bin <- factor(summary_df$DwellTimeAdvantage_bin, 
                                            levels = 1:5, 
                                            labels = c("E>>S", "E>S", "E~S", "S>E", "S>>E"))

# colours for OV levels (low, medium, high)
colors <- c("low" = "darkorchid1", "medium" = "darkorchid3", "high" = "darkmagenta")

p <- ggplot(summary_df, aes(x = DwellTimeAdvantage_bin, y = p_choose_right, 
                            group = OVcate_2, color = OVcate_2)) +
  geom_point(size = 4) +  
  geom_line(linewidth = 1.2) +  
  geom_errorbar(aes(ymin = p_choose_right - ci, ymax = p_choose_right + ci), 
                width = 0.2, linewidth = 0.8) +  
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray50", linewidth = 1) +  
  scale_color_manual(values = colors, name = "OV Level") +  
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    axis.line = element_line(color = "black", linewidth = 0.8),  
    legend.position = "top",
    legend.text = element_text(size = 18),  
    legend.title = element_text(size = 18),
    axis.text = element_text(size = 19, color = "black"), 
    axis.title = element_text(size = 20, color = "black"),  
    plot.title = element_text(size = 19, hjust = 0.5,color = "black"), 
    plot.background = element_rect(fill = "white", color = "white") 
  ) +
  labs(
    title = "Dwell-Time Advantage on Choice - ES Phase",
    x = "Dwell Time Advantage (S > E)",
    y = "P(Choose Symbolic)"
  )

ggsave("D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/ES_DTA.pdf", 
       plot = p, width = 5, height = 6, device = "pdf", bg = "white"
       )

print(p)


############### statistical analysis #####################################################################################

# group by subject and get prob. chosign right per bin
agg_data <- data %>%
  group_by(sub_id, DwellTimeAdvantage_bin, OVcate_2) %>%
  summarise(mean_p_choose_right = mean(chose_right, na.rm = TRUE), .groups = 'drop')
  
agg_data <- agg_data %>%
  mutate(
    DTA_num = as.numeric(DwellTimeAdvantage_bin)
  )

trend_model <- lmer(
  mean_p_choose_right ~ poly(DTA_num, 2, raw = FALSE) + (1 | sub_id),
  data = agg_data
)

summary(trend_model)



anova_results <- list()  # Store ANOVA results

lmm_model <- lmer(mean_p_choose_right ~ OVcate_2 * DwellTimeAdvantage_bin + (1 | sub_id),
                  data = agg_data)

anova(lmm_model)

# Post-hoc for OVcate_2 within each DwellTimeAdvantage_bin
posthoc_results <- emmeans(lmm_model, pairwise ~ OVcate_2 | DwellTimeAdvantage_bin, adjust = "bonferroni")
print(posthoc_results)


# results folder
results_file <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/ES_DwelltimeAdvantage_Results.txt"
sink(results_file) 

cat("\n ### Polynomial Trend Mixed Model (DTA bin) ###\n")
print(summary(trend_model))
cat("\n ### ANOVA: Effect of DwellTimeAdvantage_bin on P(Choose Right) ###\n")
print(anova_result)
cat("\n ### Post-hoc Tests: Pairwise Comparisons for DwellTimeAdvantage_bin ### \n")
print(posthoc_result1)
cat("\n ### Linear Mixed Model: OVcate_2 * DwellTimeAdvantage_bin Effect ### \n")
print(anova(lmm_model))
cat("\n ### Post-hoc Comparisons for OV Levels within Each Bin (LMM) ### \n")
print(posthoc_results)
sink()
cat("\n results saved to:", results_file, "\n")

# mean P(choose right) per bin for each participant
agg_data <- data %>%
  group_by(sub_id, DwellTimeAdvantage_bin) %>%
  summarise(mean_p_choose_right = mean(chose_right, na.rm = TRUE), .groups = 'drop')

anova_res <- ezANOVA(
  data = agg_data,
  dv = mean_p_choose_right,  
  wid = sub_id,              
  within = DwellTimeAdvantage_bin,  
  type = 3,               
  detailed = TRUE
)

anova_res

# post-hoc pairwise comparisons with Bonferroni cor
posthoc_result1 <- emmeans(
  lm(mean_p_choose_right ~ factor(DwellTimeAdvantage_bin), data = agg_data),  
  pairwise ~ DwellTimeAdvantage_bin,  
  adjust = "bonferroni"  
)

posthoc_result1

```
# ES Dwelltime Advantge without OV
```{r}

data <- read.csv(file)

# phase ES
phase_filter <- "ES"
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

# Basic filtering
data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(DwellTimeAdvantage, chose_right)

# Additional dwell time filtering
data <- data %>% 
  filter(
    phase == phase_filter,
    !sub_id %in% excluded_subjects,
    DwellRight > 0,        
    DwellLeft  > 0   # this can be adjusted in case we would like specific filters (or not)
  ) %>% 
  drop_na(DwellTimeAdvantage, chose_right)


# Quantile Binning of DwellTimeAdvantage (per subject, collapsed across OV)
data <- data %>%
  group_by(sub_id) %>%
  mutate(
    DwellTimeAdvantage_bin = cut(
      DwellTimeAdvantage,
      breaks = unique(quantile(
        DwellTimeAdvantage,
        probs = seq(0, 1, length.out = 6),
        na.rm = TRUE
      )),
      labels = 1:(length(unique(quantile(
        DwellTimeAdvantage,
        probs = seq(0, 1, length.out = 6),
        na.rm = TRUE
      ))) - 1),
      include.lowest = TRUE
    )
  ) %>%
  ungroup()


summary_df <- data %>%
  group_by(DwellTimeAdvantage_bin) %>%
  summarise(
    p_choose_right = mean(chose_right, na.rm = TRUE),
    ci = 1.96 * sd(chose_right, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# bin order / labels
summary_df$DwellTimeAdvantage_bin <- factor(
  summary_df$DwellTimeAdvantage_bin,
  levels = 1:5,
  labels = c("E>>S", "E>S", "E~S", "S>E", "S>>E")
)


p <- ggplot(summary_df,
            aes(x = DwellTimeAdvantage_bin,
                y = p_choose_right,
                group = 1)) +
  geom_point(size = 4, color = "darkorchid") +
  geom_line(linewidth = 1.2, color = "darkorchid") +
  geom_errorbar(
    aes(ymin = p_choose_right - ci,
        ymax = p_choose_right + ci),
    width = 0.2,
    linewidth = 0.8,
    color = "darkorchid"   # can be black as well
  ) +
  geom_hline(
    yintercept = 0.5,
    linetype = "dotted",
    color = "gray50",
    linewidth = 1
  ) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.8),
    legend.position = "none",
    axis.text = element_text(size = 19, color = "black"),
    axis.title = element_text(size = 20, color = "black"),
    plot.title = element_text(size = 19, hjust = 0.5, color = "black"),
    plot.background = element_rect(fill = "white", color = "white")
  ) +
  labs(
    title = "Dwell-Time Advantage on Choice - ES Phase",
    x = "Dwell Time Advantage (S > E)",
    y = "P(Choose Symbolic)"
  )

ggsave(
  "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/ES_DTA_no_OV.pdf",
  plot = p,
  width = 5,
  height = 6,
  device = "pdf",
  bg = "white"
)

print(p)


# Mean P(choose right) per bin for each participant
agg_data <- data %>%
  group_by(sub_id, DwellTimeAdvantage_bin) %>%
  summarise(
    mean_p_choose_right = mean(chose_right, na.rm = TRUE),
    .groups = "drop"
  )

# Numeric bin index for trend modelling
agg_data <- agg_data %>%
  mutate(
    DTA_num = as.numeric(DwellTimeAdvantage_bin)
  )

# Polynomial trend across bins
trend_model <- lmer(
  mean_p_choose_right ~ poly(DTA_num, 2, raw = FALSE) + (1 | sub_id),
  data = agg_data
)

summary(trend_model)

agg_data_anova <- agg_data %>%
  group_by(sub_id) %>%
  filter(n_distinct(DwellTimeAdvantage_bin) == 5) %>%
  ungroup()

anova_res <- ezANOVA(
  data = agg_data_anova,
  dv = mean_p_choose_right,
  wid = sub_id,
  within = DwellTimeAdvantage_bin,
  type = 3,
  detailed = TRUE
)

summary(anova_res)

posthoc_result1 <- emmeans(
  lm(mean_p_choose_right ~ factor(DwellTimeAdvantage_bin), data = agg_data_anova),
  pairwise ~ DwellTimeAdvantage_bin,
  adjust = "bonferroni"
)

posthoc_result1


results_file <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/ES_DwelltimeAdvantage_Results_no_OV.txt"

sink(results_file)

cat("\n ### Polynomial Trend Mixed Model (DTA bin) ###\n")
print(summary(trend_model))

cat("\n ### ANOVA: Effect of DwellTimeAdvantage_bin on P(Choose Right) ###\n")
print(anova_res)

cat("\n### Post-hoc Tests: Pairwise Comparisons for DwellTimeAdvantage_bin ###\n")
print(posthoc_result1)

sink()
```


# ES - p(E vs S) per rtime bin

```{r}
data <- read.csv(file)

# phase ES
phase_filter <- "ES"
excluded_subjects <- c(6,99)    # 1, 4, 5, 6, 14, 99

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects,
         rtime >= 0.250,
         rtime <= 1000 ) %>%
  drop_na(DwellTimeAdvantage, OVcate_2, chose_right)

data <- data %>%
  group_by(sub_id, OVcate_2) %>%
  mutate(rtime_bin = cut(rtime, 
                         breaks = unique(quantile(rtime, probs = seq(0, 1, length.out = 6), na.rm = TRUE)), 
                         labels = 1:(length(unique(quantile(rtime, probs = seq(0, 1, length.out = 6), na.rm = TRUE))) - 1),
                         include.lowest = TRUE)) %>%
  ungroup()


agg <- data %>%
  group_by(sub_id, rtime_bin) %>%
  summarise(
    p_E = mean(chose_right == 0, na.rm = TRUE),
    p_S = mean(chose_right == 1, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(cols = c(p_E, p_S),
               names_to  = "Choice",
               values_to = "prob") %>%
  mutate(Choice = factor(Choice,
                         levels = c("p_E", "p_S"),
                         labels = c("E", "S")))


summary_df <- agg %>%
  group_by(rtime_bin, Choice) %>%
  summarise(
    mean_prob = mean(prob, na.rm = TRUE),
    sem       = sd(prob,  na.rm = TRUE) / sqrt(n()),   # SEM, can also do SD
    .groups   = "drop"
  )

summary_df$rtime_bin <- factor(
  summary_df$rtime_bin,
  levels = 1:5,
  labels = c("0-20%", "20-40%", "40-60%", "60-80%", "80-100%")
)

p <- ggplot(
  summary_df,
  aes(x = rtime_bin,
      y = mean_prob,
      fill = Choice)  
) +
  geom_col(
    position = position_dodge(width = 0.8),
    width = 0.7
  ) +
  geom_errorbar(
    aes(ymin = mean_prob - sem,
        ymax = mean_prob + sem),
    position = position_dodge(width = 0.8),
    width = 0.2,
    linewidth = 0.7
  ) +
  # reference line at 0.5
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  scale_fill_manual(
    values = c("E" = "deepskyblue", "S" = "darkorchid"),
    name   = "Chosen option"
  ) +
  labs(
    title = "Probability of Choosing E vs S-Option by Reaction Time Quintile",
    x     = "RT Bin (shortest to longest RT)",
    y     = "Probability"
  ) +
  coord_cartesian(ylim = c(0.30, 0.70)) +
  theme_minimal(base_size = 15) +
  theme(
    legend.position   = c(0.85, 0.90),
    legend.background = element_rect(fill = "white", color = NA),
    legend.key        = element_rect(fill = NA, color = NA),
    legend.title      = element_text(size = 16),
    legend.text       = element_text(size = 16),
    axis.line         = element_line(colour = "black"),
    panel.grid.major  = element_blank(),
    panel.grid.minor  = element_blank(),
    axis.text.x       = element_text(color = "black", size = 16),
    axis.text.y       = element_text(color = "black", size = 18),
    axis.title.x      = element_text(size = 18),
    axis.title.y      = element_text(size = 18)
  )

#ggsave(
#  "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/Figures/ES_rtimeAdvantage_E_vs_S_bars.pdf",
#  plot   = p,
#  width  = 6,
#  height = 5,
#  device = "pdf",
#  bg     = "white"
#)

print(p)


# GLM

data$chose_E <- ifelse(data$chose_right == 0, 1, 0)
data$rtime_bin <- factor(data$rtime_bin)

# Model with no overall intercept to get log-odds of choosing E per bin
model <- glmer(chose_E ~ 0 + rtime_bin + (1 | sub_id),
               data = data,
               family = binomial)
em_logit <- as.data.frame(summary(emmeans(model, ~ rtime_bin)))
em_prob <- as.data.frame(summary(emmeans(model, ~ rtime_bin), type = "response"))
em_link <- summary(emmeans(model, ~ rtime_bin),
                   infer = c(TRUE, TRUE))   
em_resp <- summary(emmeans(model, ~ rtime_bin),
                   type  = "response",
                   infer = c(TRUE, TRUE)) 

em_link
em_resp

```



# GLMM - chocie E vs S per RT bin
```{r}

data <- read.csv(file)

excluded_subjects <- c(6,99)  # this here is variable (one could also exclude the participants that have missing data in the eye-tracking code - theese would be more)

data <- read.csv(file) %>%
  filter(phase == "ES",
         !sub_id %in% excluded_subjects,
         rtime >= 0.250,   # >= 250 ms
         rtime <= 1000) %>% # I don't really have an upper cut off
  drop_na(DwellTimeAdvantage, OVcate_2, chose_right) %>%
  mutate(
    chooseE = as.integer(chose_right == 0),
    log_rtime = scale(log(rtime)) # log + z-scale for stability
  )

m <- glmer(chooseE ~ log_rtime + (1|sub_id),
           data = data,
           family = binomial)

q_edges <- quantile(data$log_rtime, probs = seq(0,1,length.out=6))
q_mid <- (head(q_edges,-1) + tail(q_edges,-1)) / 2

preds <- emmeans(m, ~ log_rtime,
                 at = list(log_rtime = q_mid),
                 type = "response")

tests <- contrast(
  emmeans(m, ~ log_rtime, at = list(log_rtime = q_mid), type="link"),
  method="eff"
)
summary(tests, infer=TRUE)

preds_resp <- summary(preds)
preds_resp$prob_percent <- round(preds_resp$prob * 100, 1)
preds_resp
```
# fixation by fixation 
```{r}

MAX_BACK <- 4   # or 3
excluded_subjects <- c(1,4, 5, 6, 14, 99)

dat <- read.csv(file)
es <- dat %>%
  filter(phase == "ES", !sub_id %in% excluded_subjects) %>%
  drop_na(sub_id, rtime, Fixations)

# Fixation pars
parse_fixes <- function(x){
  if (is.null(x) || is.na(x) || x=="") return(NULL)
  if (is.list(x)) return(as.data.frame(x))
  try1 <- tryCatch(fromJSON(x, simplifyDataFrame=TRUE), error=function(e) NULL)
  if (!is.null(try1)) return(as.data.frame(try1))
  x2 <- gsub("'", "\"", x)
  try2 <- tryCatch(fromJSON(x2, simplifyDataFrame=TRUE), error=function(e) NULL)
  if (!is.null(try2)) return(as.data.frame(try2))
  NULL
}

gather_fixseq <- function(fix_str, rt_sec, back_cap=MAX_BACK){
  fx <- parse_fixes(fix_str)
  if (is.null(fx) || nrow(fx)==0 || !all(c("start_time","roi") %in% names(fx))) return(character(0))
  fx <- fx %>% arrange(start_time)
  t0 <- fx$start_time[1]; rt_ms <- rt_sec * 1000
  usable <- fx %>%
    mutate(rel_start = start_time - t0) %>%
    filter(rel_start <= rt_ms, roi %in% c(1,2))
  if (nrow(usable) == 0) return(character(0))
  lab <- ifelse(usable$roi == 1, "E", "S")
  rev(lab)[seq_len(min(length(lab), back_cap + 1))]
}

# long table
es_seq <- es %>%
  mutate(fix_seq = map2(Fixations, rtime, gather_fixseq)) %>%
  filter(map_int(fix_seq, length) > 1)

fix_long <- es_seq %>%
  transmute(sub_id,
            fix_idx_list = map(fix_seq, ~ seq(0, length(.x) - 1)),
            label_list   = fix_seq) %>%
  unnest(c(fix_idx_list, label_list)) %>%
  rename(fix_idx = fix_idx_list, label = label_list) %>%
  filter(fix_idx <= MAX_BACK) %>%
  mutate(label = factor(label, levels = c("S", "E")),  # S is reference
         y = as.integer(label == "E"))

# Overall mean and SD
overall_fix_stats <- fix_long %>%
  summarise(
    mean_E = mean(y),   # proportion of fixations on E
    sd_E   = sd(y),     
    n      = n()
  )

print(overall_fix_stats)

# Mean and SD per fixation index (0 = last fixation, 1 = one back etc)
fixidx_fix_stats <- fix_long %>%
  group_by(fix_idx) %>%
  summarise(
    mean_E = mean(y),
    sd_E   = sd(y),
    n      = n(),
    .groups = "drop"
  )

print(fixidx_fix_stats)

#Fix model
model_results <- map_dfr(0:MAX_BACK, function(idx) {
  df_i <- fix_long %>%
    filter(fix_idx == idx) %>%
    filter(!sub_id %in% excluded_subjects)

  model <- tryCatch(
    glmer(label ~ 1 + (1 | sub_id), data = df_i, family = binomial)
  )

  tidy(model, effects = "fixed") %>%
    mutate(fix_idx = idx, x = ifelse(idx == 0, 0, -idx))
})

# Format
ttests <- model_results %>%
  transmute(
    fix_idx,
    x,
    beta    = estimate,
    se      = std.error,
    z       = statistic,
    p_raw   = p.value
  ) %>%
  mutate(p_fdr = p.adjust(p_raw, method = "BH")) %>%
  arrange(fix_idx)

print(ttests, n = Inf)

```

`

# fixation by fixation - EE phase

```{r}
MAX_BACK <- 4
excluded_subjects <- c(1,4, 5, 6, 14, 99)

dat <- read.csv(file)
es <- dat %>%
  filter(phase == "EE", !sub_id %in% excluded_subjects) %>%
  drop_na(sub_id, rtime, Fixations)

parse_fixes <- function(x){
  if (is.null(x) || is.na(x) || x=="") return(NULL)
  if (is.list(x)) return(as.data.frame(x))
  try1 <- tryCatch(fromJSON(x, simplifyDataFrame=TRUE), error=function(e) NULL)
  if (!is.null(try1)) return(as.data.frame(try1))
  x2 <- gsub("'", "\"", x)
  try2 <- tryCatch(fromJSON(x2, simplifyDataFrame=TRUE), error=function(e) NULL)
  if (!is.null(try2)) return(as.data.frame(try2))
  NULL
}

gather_fixseq <- function(fix_str, rt_sec, back_cap=MAX_BACK){
  fx <- parse_fixes(fix_str)
  if (is.null(fx) || nrow(fx)==0 || !all(c("start_time","roi") %in% names(fx))) return(character(0))
  fx <- fx %>% arrange(start_time)
  t0 <- fx$start_time[1]; rt_ms <- rt_sec * 1000
  usable <- fx %>%
    mutate(rel_start = start_time - t0) %>%
    filter(rel_start <= rt_ms, roi %in% c(1,2))
  if (nrow(usable) == 0) return(character(0))
  lab <- ifelse(usable$roi == 1, "left", "right")
  rev(lab)[seq_len(min(length(lab), back_cap + 1))]
}

es_seq <- es %>%
  mutate(fix_seq = map2(Fixations, rtime, gather_fixseq)) %>%
  filter(map_int(fix_seq, length) > 1)

fix_long <- es_seq %>%
  transmute(sub_id,
            fix_idx_list = map(fix_seq, ~ seq(0, length(.x) - 1)),
            label_list   = fix_seq) %>%
  unnest(c(fix_idx_list, label_list)) %>%
  rename(fix_idx = fix_idx_list, label = label_list) %>%
  filter(fix_idx <= MAX_BACK) %>%
  mutate(label = factor(label, levels = c("right", "left")),  # S is reference
         y = as.integer(label == "left"))

overall_fix_stats <- fix_long %>%
  summarise(
    mean_left = mean(y),   # proportion of fixations on E
    sd_left   = sd(y),    
    n      = n()
  )

print(overall_fix_stats)

# Mean and SD per fixation index (0 = last fixation, 1 = one back, etc.)
fixidx_fix_stats <- fix_long %>%
  group_by(fix_idx) %>%
  summarise(
    mean_left = mean(y),
    sd_left   = sd(y),
    n      = n(),
    .groups = "drop"
  )

print(fixidx_fix_stats)

# label == dependent variable
model_results <- map_dfr(0:MAX_BACK, function(idx) {
  df_i <- fix_long %>%
    filter(fix_idx == idx) %>%
    filter(!sub_id %in% excluded_subjects)  

  if (n_distinct(df_i$sub_id) < 6) return(NULL) 
  
  model <- tryCatch(
    glmer(label ~ 1 + (1 | sub_id), data = df_i, family = binomial),
    error = function(e) NULL
  )
  
  if (is.null(model)) return(NULL)
  
  tidy(model, effects = "fixed") %>%
    mutate(fix_idx = idx, x = ifelse(idx == 0, 0, -idx))
})

ttests <- model_results %>%
  transmute(
    fix_idx,
    x,
    beta    = estimate,
    se      = std.error,
    z       = statistic,
    p_raw   = p.value
  ) %>%
  mutate(p_fdr = p.adjust(p_raw, method = "BH")) %>%
  arrange(fix_idx)

print(ttests, n = Inf)

```


# mean nr of fixtions - ES phase
```{r}
es_seq <- es %>%
  mutate(fix_seq = map2(Fixations, rtime, gather_fixseq)) %>%
  filter(map_int(fix_seq, length) > 1)

es_seq <- es_seq %>%
  mutate(n_fix = map_int(fix_seq, length))

mean_fixations <- mean(es_seq$n_fix)
sd_fixations <- sd(es_seq$n_fix)
median_fixations <- median(es_seq$n_fix)

mean_fixations
sd_fixations
```

# ES - gaze difference per bin

```{r}

file_path <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/data/data_sets/GarciaParticipants_Eye_Response_Feed_Allfix_addm_OV_Abs_CCT.csv"

data <- read.csv(file)
phase_filter <- "ES"
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(DwellTimeAdvantage, OVcate_2, chose_right)  

data$OVcate_2 <- factor(data$OVcate_2, levels = c("low", "medium", "high"))

data2 <- data %>%
  mutate(DwellTimeAdvantage_abs = abs(DwellTimeAdvantage)) %>%
  group_by(sub_id, OVcate_2) %>%
  mutate(
    DwellTimeAdvantage_bin = cut(
      DwellTimeAdvantage,
      breaks = unique(quantile(DwellTimeAdvantage,
                               probs = seq(0, 1, length.out = 6),
                               na.rm = TRUE)),
      labels = 1:(length(unique(quantile(DwellTimeAdvantage,
                                         probs = seq(0, 1, length.out = 6),
                                         na.rm = TRUE))) - 1),
      include.lowest = TRUE
    )
  ) %>%
  ungroup() %>%
  mutate(
    DwellTimeAdvantage_bin = factor(
      DwellTimeAdvantage_bin,
      levels = 1:5,
      labels = c("E>>S", "E>S", "E~S", "S>E", "S>>E")
    )
  )

colors <- c("low" = "darkorchid1", "medium" = "darkorchid3", "high" = "darkmagenta")

subject_summary <- data2 %>%
  group_by(sub_id, OVcate_2, DwellTimeAdvantage_bin) %>%
  summarise(
    mean_abs = mean(DwellTimeAdvantage_abs, na.rm = TRUE),
    .groups  = "drop"
  )

group_summary2 <- subject_summary %>%
  group_by(OVcate_2, DwellTimeAdvantage_bin) %>%
  summarise(
    Mean = mean(mean_abs),
    SEM  = sd(mean_abs) / sqrt(n()),
    .groups = "drop"
  )
ggplot() +
    geom_col(
    data     = group_summary2,
    aes(
      x    = DwellTimeAdvantage_bin,
      y    = Mean,
      fill = OVcate_2
    ),
    color    = "black",
    position = position_dodge(width = 0.9),
    width    = 0.7
  ) +
    geom_errorbar(
    data     = group_summary2,
    aes(
      x      = DwellTimeAdvantage_bin,
      ymin   = Mean - SEM,
      ymax   = Mean + SEM,
      group  = OVcate_2
    ),
    position = position_dodge(width = 0.9),
    width    = 0.2
  ) +
    geom_point(
    data     = subject_summary,
    aes(
      x     = DwellTimeAdvantage_bin,
      y     = mean_abs,
      group = OVcate_2
    ),
    shape    = 21,
    fill     = alpha("white", 0.6),
    color    = "black",
    size     = 2,
    position = position_dodge(width = 0.9)
  ) +
    scale_fill_manual(
    name   = "OV Level",
    values = colors
  ) +
  labs(
    title = "Mean Absolute Dwell-Time by Advantage Bin & OV Level",
    x     = "Dwell-Time Advantage Bin",
    y     = "Mean Absolute Dwell-Time (ms)"
  ) +
  theme_classic() +
  theme(
    legend.position = "top",
    axis.text  = element_text(size = 14),
    axis.title = element_text(size = 16)
  )


```

#EE gaze difference per bin

```{r}

file_path <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/data/data_sets/GarciaParticipants_Eye_Response_Feed_Allfix_addm_OV_Abs_CCT.csv"

data <- read.csv(file_path)
phase_filter <- "EE"
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(DwellTimeAdvantage, OVcate_2, chose_right)  

data$OVcate_2 <- factor(data$OVcate_2, levels = c("low", "medium", "high"))

data2 <- data %>%
  mutate(DwellTimeAdvantage_abs = abs(DwellTimeAdvantage)) %>%
  group_by(sub_id, OVcate_2) %>%
  mutate(
    DwellTimeAdvantage_bin = cut(
      DwellTimeAdvantage,
      breaks = unique(quantile(DwellTimeAdvantage,
                               probs = seq(0, 1, length.out = 6),
                               na.rm = TRUE)),
      labels = 1:(length(unique(quantile(DwellTimeAdvantage,
                                         probs = seq(0, 1, length.out = 6),
                                         na.rm = TRUE))) - 1),
      include.lowest = TRUE
    )
  ) %>%
  ungroup() %>%
  mutate(
    DwellTimeAdvantage_bin = factor(
      DwellTimeAdvantage_bin,
      levels = 1:5,
      labels = c("L>>R", "L>R", "L ~ R", "R>L", "R>>L")
    )
  )

colors <- c("low" = "blue", "medium" = "deepskyblue", "high" = "navy")   # blue , deepskyblue navy

subject_summary <- data %>%
  group_by(sub_id, OVcate_2, DwellTimeAdvantage_bin) %>%
  summarise(
    mean_abs = mean(DwellTimeAdvantage_abs, na.rm = TRUE),
    .groups  = "drop"
  )

group_summary2 <- subject_summary %>%
  group_by(OVcate_2, DwellTimeAdvantage_bin) %>%
  summarise(
    Mean = mean(mean_abs),
    SEM  = sd(mean_abs) / sqrt(n()),
    .groups = "drop"
  )
ggplot() +
    geom_col(
    data     = group_summary2,
    aes(
      x    = DwellTimeAdvantage_bin,
      y    = Mean,
      fill = OVcate_2
    ),
    color    = "black",
    position = position_dodge(width = 0.9),
    width    = 0.7
  ) +
    geom_errorbar(
    data     = group_summary2,
    aes(
      x      = DwellTimeAdvantage_bin,
      ymin   = Mean - SEM,
      ymax   = Mean + SEM,
      group  = OVcate_2
    ),
    position = position_dodge(width = 0.9),
    width    = 0.2
  ) +
    geom_point(
    data     = subject_summary,
    aes(
      x     = DwellTimeAdvantage_bin,
      y     = mean_abs,
      group = OVcate_2
    ),
    shape    = 21,
    fill     = alpha("white", 0.6),
    color    = "black",
    size     = 2,
    position = position_dodge(width = 0.9)
  ) +
  
  # Your custom colours
  scale_fill_manual(
    name   = "OV Level",
    values = colors
  ) +
  
  labs(
    title = "Mean Absolute Dwell-Time by Advantage Bin & OV Level",
    x     = "Dwell-Time Advantage Bin",
    y     = "Mean Absolute Dwell-Time (ms)"
  ) +
  
  theme_classic() +
  theme(
    legend.position = "top",
    axis.text  = element_text(size = 14),
    axis.title = element_text(size = 16)
  )

```



# EE - Dwell-Time Advantage

```{r}
data <- read.csv(file)
phase_filter <- "EE"
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(DwellTimeAdvantage, OVcate_2, chose_right)  

data$OVcate_2 <- factor(data$OVcate_2, levels = c("low", "medium", "high"))

data <- data %>%
  group_by(sub_id, OVcate_2) %>%
  mutate(DwellTimeAdvantage_bin = cut(DwellTimeAdvantage, 
                                      breaks = unique(quantile(DwellTimeAdvantage, probs = seq(0, 1, length.out = 6), na.rm = TRUE)), 
                                      labels = 1:(length(unique(quantile(DwellTimeAdvantage, probs = seq(0, 1, length.out = 6), na.rm = TRUE))) - 1),
                                      include.lowest = TRUE)) %>%
  ungroup()


summary_df <- data %>%
  group_by(DwellTimeAdvantage_bin, OVcate_2) %>%
  summarise(
    p_choose_right = mean(chose_right, na.rm = TRUE),
    ci = 1.96 * sd(chose_right, na.rm = TRUE) / sqrt(n()),  # 95% CI
    .groups = 'drop'
  )

summary_df$DwellTimeAdvantage_bin <- factor(summary_df$DwellTimeAdvantage_bin, levels = 1:5, labels = c("L>>R", "L>R", "L ~ R", "R>L", "R>>L"))

colors <- c("low" = "deepskyblue", "medium" = "blue", "high" = "navy")   


p <- ggplot(summary_df, aes(x = DwellTimeAdvantage_bin, y = p_choose_right, 
                            group = OVcate_2, color = OVcate_2)) +
  geom_point(size = 4) +  
  geom_line(linewidth = 1.2) +  
  geom_errorbar(aes(ymin = p_choose_right - ci, ymax = p_choose_right + ci), 
                width = 0.2, linewidth = 0.8) +  
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray50", linewidth = 1) +  
  scale_color_manual(values = colors, name = "OV Level") +  
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    axis.line = element_line(color = "black", linewidth = 0.8),  
    legend.position = "top",
    legend.text = element_text(size = 18),  
    legend.title = element_text(size = 18),
    axis.text = element_text(size = 18, color = "black"), 
    axis.title = element_text(size = 20, color = "black"),  
    plot.title = element_text(size = 19, hjust = 0.5,color = "black"), 
    plot.background = element_rect(fill = "white", color = "white") 
  ) +
  labs(
    title = "Dwell-Time Advantage on Choice - EE-Phase",
    x = "Dwell Time Advantage (R > L)",
    y = "P(Choose Right)"
  )

ggsave("D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/EE_DTA.pdf", 
       plot = p, width = 5, height = 6, device = "pdf", bg = "white"
       )

print(p)



agg_data <- data %>%
  group_by(sub_id, DwellTimeAdvantage_bin, OVcate_2) %>%
  summarise(mean_p_choose_right = mean(chose_right, na.rm = TRUE), .groups = 'drop')
anova_results <- list()  

lmm_model <- lmer(mean_p_choose_right ~ OVcate_2 * DwellTimeAdvantage_bin + (1 | sub_id),
                  data = agg_data)
anova(lmm_model)

# post hoc
posthoc_results <- emmeans(lmm_model, pairwise ~ OVcate_2 | DwellTimeAdvantage_bin, adjust = "bonferroni")
print(posthoc_results)


results_file <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/EE_DwelltimeAdvantage_Results.txt"
sink(results_file) 

cat("\n### ANOVA: Effect of DwellTimeAdvantage_bin on P(Choose Right) ###\n")
print(anova_result)
cat("\n### Post-hoc Tests: Pairwise Comparisons for DwellTimeAdvantage_bin ###\n")
print(posthoc_result1)
cat("\n### Linear Mixed Model: OVcate_2 * DwellTimeAdvantage_bin Effect ###\n")
print(anova(lmm_model))
cat("\n### Post-hoc Comparisons for OV Levels within Each Bin (LMM) ###\n")
print(posthoc_results)
sink()
cat("\n results saved to:", results_file, "\n")

# mean P(choose right) per bin for each participant
agg_data <- data %>%
  group_by(sub_id, DwellTimeAdvantage_bin) %>%
  summarise(mean_p_choose_right = mean(chose_right, na.rm = TRUE), .groups = 'drop')

#anova_res <- ezANOVA(
#  data = agg_data,
#  dv = mean_p_choose_right,  
#  wid = sub_id,              
#  within = DwellTimeAdvantage_bin,  
#  type = 3,               
#  detailed = TRUE
#)

#anova_res

# post-hoc pairwise comparisons with Bonferroni cor
posthoc_result1 <- emmeans(
  lm(mean_p_choose_right ~ factor(DwellTimeAdvantage_bin), data = agg_data),  
  pairwise ~ DwellTimeAdvantage_bin,  
  adjust = "bonferroni"  
)

posthoc_result1


```

# ES - Final fixations on choice per VD and OV

```{r}

data <- read.csv(file_path)
phase_filter <- "ES" 
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(FinalFixLoc, OVcate_2, chose_right, p1, p2)  

data$OVcate_2 <- factor(data$OVcate_2, levels = c("low", "medium", "high"))

# convert FinalFixLoc to categorical Right or Left
data$FinalFixLocBinary <- ifelse(data$FinalFixLoc == 2, "S", "E")
data$FinalFixLocBinary <- factor(data$FinalFixLocBinary, levels = c("E", "S"))

# value difference
data$ValueDifference <- round(data$p2 - data$p1, 1)

data <- data %>%
  group_by(sub_id) %>%
  mutate(ValueDifference_bin = cut(ValueDifference, breaks = unique(quantile(ValueDifference, probs = seq(0, 1, length.out = 6), na.rm = TRUE)),
                                   labels = c("E>>S", "E>S", "E ~ S", "S>E", "S>>E"),
                                   include.lowest = TRUE)) %>%
  ungroup()

summary_df <- data %>%
  group_by(ValueDifference_bin, OVcate_2, FinalFixLocBinary) %>%
  summarise(
    p_choose_right = mean(chose_right, na.rm = TRUE),
    ci = 1.96 * sd(chose_right, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

print(summary_df)


colors <- c("low" = "darkorchid1", "medium" = "darkorchid3", "high" = "darkmagenta")  

summary_df$FinalFixLocBinary <- factor(summary_df$FinalFixLocBinary,
                                        levels = c("E", "S"),
                                        labels = c("Line: E", "Dotted: S"))
line_types <- c("Line: E" = "solid", "Dotted: S" = "dashed")


summary_df$OV_label <- summary_df$OVcate_2
summary_df$Fix_label <- summary_df$FinalFixLocBinary

p <- ggplot(summary_df, aes(x = ValueDifference_bin, y = p_choose_right,
                            group = interaction(Fix_label, OV_label),
                            color = OV_label, linetype = Fix_label)) +
  geom_point(size = 3, position = position_dodge(width = 0.2)) +  
  geom_line(position = position_dodge(width = 0.2), linewidth = 1.2) +  
  geom_errorbar(aes(ymin = p_choose_right - ci, ymax = p_choose_right + ci),
                width = 0.2, linewidth = 0.8, position = position_dodge(width = 0.2)) +  
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray50", linewidth = 1) +  

  scale_color_manual(values = colors, name = "OV Level") +  
  scale_linetype_manual(
    values = line_types,
    name = "Final Fixation",
    guide = guide_legend(
      override.aes = list(linetype = c(0, 0))  
    )
  ) +

  guides(
    linetype = guide_legend(order = 1),
    color    = guide_legend(order = 2)
  ) +

  theme_minimal(base_size = 10) +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    axis.line = element_line(color = "black", linewidth = 0.8), 
    legend.position = "top",
    legend.box = "vertical",
    legend.text = element_text(size = 17),  
    legend.title = element_text(size = 17),  
    legend.spacing.y = unit(-0.2, "cm"),   # reduce vertical spacing
    axis.text = element_text(size = 19, color = "black"),  
    axis.title = element_text(size = 20, color = "black"),  
    plot.title = element_text(size = 19, hjust = 0.5, color = "black"),  
    plot.background = element_rect(fill = "white", color = "white") 
  ) +
  labs(
    title = paste("Final Fixation Effect on Choice -", phase_filter, "Phase"),
    x = "Value Difference (S > E)",
    y = "P(Choose Symbol)"
  )


#ggsave(paste0("D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metrics_OV_Abs/", #phase_filter, "_FinalFix.pdf"), 
#      plot = p, width = 5, height = 6, device = "pdf", bg = "white")

p

agg_data <- data %>%
  group_by(sub_id, ValueDifference_bin, FinalFixLocBinary, OVcate_2) %>%
  summarise(mean_p_choose_right = mean(chose_right, na.rm = TRUE), .groups = 'drop')


anova_results <- list()  

lmm_model <- lmer(mean_p_choose_right ~ OVcate_2 * ValueDifference_bin * FinalFixLocBinary + (1 | sub_id),
                  data = agg_data)

anova(lmm_model)

# post hoc
posthoc_results <- emmeans(lmm_model, pairwise ~ OVcate_2 | ValueDifference_bin * FinalFixLocBinary, adjust = "bonferroni")
print(posthoc_results)


#results_file <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/ES_FinalFixations_#Results.txt"
#sink(results_file) 



cat("\n### ANOVA: Effect of FinalFixations_bin on P(Choose Right) ###\n")
print(anova_result)
cat("\n### Post-hoc Tests: Pairwise Comparisons for FinalFixations_bin ###\n")
print(posthoc_result1)
cat("\n### Linear Mixed Model: OVcate_2 * FinalFixations_bin Effect ###\n")
print(anova(lmm_model))
cat("\n### Post-hoc Comparisons for OV Levels within Each Bin (LMM) ###\n")
print(posthoc_results)
sink()
cat("\n results saved to:", results_file, "\n")

#anova_res <- ezANOVA(
#  data = agg_data,
#  dv = mean_p_choose_right,
#  wid = sub_id,
#  within = .(ValueDifference_bin),
#  type = 3,
#  detailed = TRUE
#)

#anova_res

# post-hoc pairwise comparisons with Bonferroni cor
posthoc_result1 <- emmeans(
  lm(mean_p_choose_right ~ factor(ValueDifference_bin), data = agg_data),  
  pairwise ~ ValueDifference_bin,  
  adjust = "bonferroni"  
)

posthoc_result1
```


# EE - Final fixations on choice per VD and OV

```{r}
data <- read.csv(file_path)
phase_filter <- "EE" 
excluded_subjects <- c(1, 4, 5, 6, 14, 99)

data <- data %>%
  filter(phase == phase_filter & !sub_id %in% excluded_subjects) %>%
  drop_na(FinalFixLoc, OVcate_2, chose_right, p1, p2)  

data$OVcate_2 <- factor(data$OVcate_2, levels = c("low", "medium", "high"))

data$FinalFixLocBinary <- ifelse(data$FinalFixLoc == 2, "R", "L")
data$FinalFixLocBinary <- factor(data$FinalFixLocBinary, levels = c("L", "R"))

data$ValueDifference <- round(data$p2 - data$p1, 1)

data <- data %>%
  group_by(sub_id) %>%
  mutate(ValueDifference_bin = cut(ValueDifference, breaks = unique(quantile(ValueDifference, probs = seq(0, 1, length.out = 6), na.rm = TRUE)),
                                   labels = c("L>>R", "L>R", "L ~ R", "R>L", "R>>L"),
                                   include.lowest = TRUE)) %>%
  ungroup()


summary_df <- data %>%
  group_by(ValueDifference_bin, OVcate_2, FinalFixLocBinary) %>%
  summarise(
    p_choose_right = mean(chose_right, na.rm = TRUE),
    ci = 1.96 * sd(chose_right, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

print(summary_df)


colors <- c("low" = "deepskyblue", "medium" = "blue", "high" = "navy")  

summary_df$FinalFixLocBinary <- factor(summary_df$FinalFixLocBinary,
                                        levels = c("L", "R"),
                                        labels = c("Line: L", "Dotted: R"))
line_types <- c("Line: L" = "solid", "Dotted: R" = "dashed")


summary_df$OV_label <- summary_df$OVcate_2
summary_df$Fix_label <- summary_df$FinalFixLocBinary

p <- ggplot(summary_df, aes(x = ValueDifference_bin, y = p_choose_right,
                            group = interaction(Fix_label, OV_label),
                            color = OV_label, linetype = Fix_label)) +
  geom_point(size = 3, position = position_dodge(width = 0.2)) +  
  geom_line(position = position_dodge(width = 0.2), linewidth = 1.2) +  
  geom_errorbar(aes(ymin = p_choose_right - ci, ymax = p_choose_right + ci),
                width = 0.2, linewidth = 0.8, position = position_dodge(width = 0.2)) +  
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray50", linewidth = 1) +  

  scale_color_manual(values = colors, name = "OV Level") +  
  scale_linetype_manual(
    values = line_types,
    name = "Final Fixation",
    guide = guide_legend(
      override.aes = list(linetype = c(0, 0))  
    )
  ) +

  guides(
    linetype = guide_legend(order = 1),
    color    = guide_legend(order = 2)
  ) +

  theme_minimal(base_size = 10) +
  theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    axis.line = element_line(color = "black", linewidth = 0.8), 
    legend.position = "top",
    legend.box = "vertical",
    legend.text = element_text(size = 17),  
    legend.title = element_text(size = 17),  
    legend.spacing.y = unit(-0.2, "cm"),   
    axis.text = element_text(size = 19, color = "black"),  
    axis.title = element_text(size = 20, color = "black"),  
    plot.title = element_text(size = 19, hjust = 0.5, color = "black"),  
    plot.background = element_rect(fill = "white", color = "white") 
  ) +
  labs(
    title = paste("Final Fixation Effect on Choice -", phase_filter, "Phase"),
    x = "Value Difference (R > L)",
    y = "P(Choose Right)"
  )


#ggsave(paste0("D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/", #phase_filter, "_FinalFix.pdf"), 
#      plot = p, width = 5, height = 6, device = "pdf", bg = "white")

p


agg_data <- data %>%
  group_by(sub_id, ValueDifference_bin, FinalFixLocBinary, OVcate_2) %>%
  summarise(mean_p_choose_right = mean(chose_right, na.rm = TRUE), .groups = 'drop')


anova_results <- list()  

lmm_model <- lmer(mean_p_choose_right ~ OVcate_2 * ValueDifference_bin * FinalFixLocBinary + (1 | sub_id),
                  data = agg_data)


anova(lmm_model)

# post hoc
posthoc_results <- emmeans(lmm_model, pairwise ~ OVcate_2 | ValueDifference_bin * FinalFixLocBinary, adjust = "bonferroni")
print(posthoc_results)


#results_file <- "D:/Aberdeen_Uni_June24/cap/THESIS/Garcia_Analysis/stats_TingGluth/R_regression_eye_metric/EE_FinalFixations_Results.txt"
#sink(results_file) 

cat("\n### ANOVA: Effect of FinalFixations_bin on P(Choose Right) ###\n")
print(anova_result)
cat("\n### Post-hoc Tests: Pairwise Comparisons for FinalFixations_bin ###\n")
print(posthoc_result1)
cat("\n### Linear Mixed Model: OVcate_2 * FinalFixations_bin Effect ###\n")
print(anova(lmm_model))
cat("\n###Post-hoc Comparisons for OV Levels within Each Bin (LMM) ###\n")
print(posthoc_results)
sink()
cat("\n results saved to:", results_file, "\n")

#anova_res <- ezANOVA(
#  data = agg_data,
#  dv = mean_p_choose_right,
#  wid = sub_id,
#  within = .(ValueDifference_bin),
#  type = 3,
#  detailed = TRUE
#)


# post-hoc pairwise comparisons with Bonferroni cor
posthoc_result1 <- emmeans(
  lm(mean_p_choose_right ~ factor(ValueDifference_bin), data = agg_data),  
  pairwise ~ ValueDifference_bin,  
  adjust = "bonferroni"  
)

posthoc_result1
```


# LMM for role of fixation and duration 

```{r}

file <- "C:/Cluster_Github/HDDM_Vero/data_sets/data_sets_Garcia/GarciaParticipants_Eye_Response_Feed_Allfix_addm_OV_Abs_CCT.csv"

excluded_subs <- c(1, 4, 5, 6, 14, 99)

df <- read_csv(file)

df <- df %>%
  mutate(sub_id = as.integer(sub_id),
         phase = toupper(phase)) %>%
  filter(phase == "ES", !(sub_id %in% excluded_subs))

# 1 = E, 2 = S
loc_to_opt <- function(x) {
  ifelse(is.na(x), NA,
         ifelse(round(x) == 1, "E",
                ifelse(round(x) == 2, "S", NA)))
}

# Durations
dur_long <- bind_rows(
  df %>% transmute(sub_id, role = "First",
                   opt_type = loc_to_opt(FirstFixLoc),
                   dur_ms = FirstFixDur),
  df %>% transmute(sub_id, role = "Middle",
                   opt_type = loc_to_opt(MiddleDominantLoc),
                   dur_ms = MiddleDominantDur),
  df %>% transmute(sub_id, role = "Final",
                   opt_type = loc_to_opt(FinalFixLoc),
                   dur_ms = FinalFixDur)
) %>%
  filter(opt_type %in% c("E","S"), !is.na(dur_ms)) %>%
  mutate(role = factor(role, levels = c("First","Middle","Final")),
         opt_type = factor(opt_type, levels = c("E","S")))

# Loc
loc_long <- bind_rows(
  df %>% transmute(sub_id, role = "First",
                   opt_type = loc_to_opt(FirstFixLoc)),
  df %>% transmute(sub_id, role = "Middle",
                   opt_type = loc_to_opt(MiddleDominantLoc)),
  df %>% transmute(sub_id, role = "Final",
                   opt_type = loc_to_opt(FinalFixLoc))
) %>%
  filter(opt_type %in% c("E","S")) %>%
  mutate(role = factor(role, levels = c("First","Middle","Final")),
         opt_type = factor(opt_type, levels = c("E","S")),
         E_fix = ifelse(opt_type == "E", 1, 0))


m_prob <- glmer(E_fix ~ role + (1 | sub_id),
                data = loc_long,
                family = binomial)
summary(m_prob)

# pairwise contrasts of E vs S 
emm_prob <- emmeans(m_prob, ~ 1 | role, type = "response")  # to get back to probabilties
emm_prob

# E vs S
# since E_fix is binary (1=E, 0=S), the intercept per role tells prob(E)
# to test against 0.5
test(emm_prob, null = 0.5, type = "response")

m_dur <- lmer(dur_ms ~ role * opt_type + (1 | sub_id),
              data = dur_long)
summary(m_dur)
emm_dur <- emmeans(m_dur, ~ opt_type | role)
contrast(emm_dur, "pairwise", by = "role")

```
